Test

### 2016-07-22 Berkeley_PD_Stop.Rmd
updated 072216

stop_df <- mutate(stop_df, Dispositions = str_extract_all(stop_df$Dispositions, "[a-zA-Z0-9]{6}"))

View(stop_df)

>>>>

#mutate dispositions column to only contain six character cases
stop_df <- mutate(stop_df, Dispositions = str_extract_all(stop_df$Dispositions, "[a-zA-Z0-9]{6}"))
#removes empty cases
stop_df <- mutate(stop_df, Dispositions = str_replace_all(stop_df$Dispositions, "character(0)", ""))

View(stop_df)
View(dispositions)
###
